Structured Versus Decorated Cospans

### 2021-06-22 cospans_new.tex
A bit more work on the intro of Section 4.

We now compare structured and decorated cospans.   In \cref{thm:decorated_cospans_1} we built a double category of decorated cospans from a functor $\Phi \maps \A/U \to \A$.    In \cref{thm:structured_cospans} we built a double category of structured cospans from a functor $\Psi \maps L/\X \to \A$.   We now show that under certain conditions $L$ is left adjoint to $U$.   Whenever this happens, $\A/U$ is isomorphic to $L/\X$, by a general fact about arrow categories.    The bifibrations $\Phi$ and $\Psi$ are then also isomorphic.   By the functoriality
of Shulman's construction in \cref{lem:shulman}, it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.

>>>>

We now compare structured and decorated cospans.   In \cref{thm:decorated_cospans_1} we built a double category of decorated cospans from a bifibration $\Phi \maps \A/U \to \A$.    In \cref{thm:structured_cospans}, we built a double category of structured cospans from a bifibration $\Psi \maps L/\X \to \A$ in a very similar way.   We now show that under certain conditions $L$ is left adjoint to $U$.   Whenever this happens, $\A/U$ is isomorphic to $L/\X$, by a simple and general fact about arrow categories.    The bifibrations $\Phi$ and $\Psi$ are also isomorphic.   By the functoriality of Shulman's construction in \cref{lem:shulman}, it follows that the double category of decorated cospans is isomorphic to the double category of structured cospans.
